A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-07-31 07_Manuscript.Rmd
Update results and hardcoded values. Remove T3 object and use actual summary of contrasts

::: {custom-style="keywords"}
**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
:::
<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->

@@

Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2). 
Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively). 
However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).

@@

@@

```{r table3_Contrasts, echo = FALSE}
T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3[,2:5] <- round(T3[,2:5], 4)
T3 %>%
   mutate(contrasts = gsub("-","",contrasts))%>%
   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
   mutate(contrasts = gsub(" = 0","",contrasts))%>%
   flextable()%>%
   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
   autofit(add_w = 0.2)%>%
   align(j = c(2,3,4), align = "center", part = "all") %>%
   set_header_labels(contrasts = "Treatment contrasts",
                     estimates = "Estimate",
                     se = "Std Error",
                     z_val = "Z-Score",
                     pval = "P-Value",
                     VisP = " ")%>%
   fontsize(size = 9)%>%
   width(j = 5,0.7)%>%
   width(j = 6, .3)
```

>>>>

::: {custom-style="keywords"}
**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
:::
<!-- Is anyone aware of a way to put the "Type of paper" text above the rendered YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
I am considering dropping the lua files and just coding in the different styles to suit the MDPI_Agronomy_Template.docx -->

@@

Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2). 
Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
The treatment that showed the most yield saved compared to the control, $Recommended_{plus}$, was also significantly higher than all other single applications, (
$Early_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Early",contrast_Ssum$contrast)])`, 
$Recommended_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Recommended",contrast_Ssum$contrast)])` and
$Late_{single}$, `r reportP(contrast_Ssum$pvals[grep("Late - Recommended_plus",contrast_Ssum$contrast)])`). 
However the $Late_{plus}$ only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`)
Consideration should be given when comparing $Late_{plus}$ and $Early_{single}$ treatments given they did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments $Late_{single}$ provided the highest yield protection, and was estimated at saving an average of `r round(PM_mv$b[5,1] * 1000, 2)` kg / ha (SE = `r round(PM_mv$se[5] * 1000, 2)` kg / ha) relative to the no spray control (`r reportP(PM_mv$pval[5])`). 
$Early_{single}$ treatments were significantly lower than all other treatments (Table 3) and reported a mean estimate `r abs(round(PM_mv$b[2,1] * 1000, 2))` kg / ha (SE = `r round(PM_mv$se[2] * 1000, 2)` kg / ha) lower than the no spray control (`r reportP(PM_mv$pval[2])`).

@@

First sign of powdery mildew was observed as early as the 28th of February in the 2013 trial at .... ; and as late as the 12th of April in the 2018 trial at ...

@@

```{r table3_Contrasts, echo = FALSE}
contrast_Ssum[,2:5] <- round(contrast_Ssum[,2:5], 4)
contrast_Ssum %>%
   slice(grep("control", contrast, invert = TRUE)) %>%
   mutate(pvals = reportP(pvals)) %>%
   mutate(pvals = gsub("P = ","",pvals)) %>%
   flextable()%>%
   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
   autofit(add_w = 0.2)%>%
   align(j = c(2:5), align = "center", part = "all") %>%
   #align(j = c(5), align = "right", part = "all") %>%
   set_header_labels(contrasts = "Treatment contrasts",
                     coefficients = "Estimate",
                     StdErr = "Std Error",
                     Zvalue = "Z-Score",
                     pvals = "P-Value",
                     sig = " ")%>%
   fontsize(size = 9)%>%
   width(j = 5,0.8)%>%
   width(j = 6, .3)
```
